Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-17 sas2015/content/concl.tex
trimming in conclusions

Previous algorithms for data-flow analysis are unable to avoid propagating
data-flow facts along infeasible paths that arise in the presence of
correlated polymorphic method calls. 
% 
We present an approach for transforming an IFDS problem into an IDE problem
in which path feasibility is encoded into the functions that are associated
with edges in an exploded control-flow supergraph. The solution to this
IDE problem can be mapped back to the solution space of the original IFDS
problem, and is more precise for some client programs because the flow of data along
infeasible paths is prevented. We present a formalization of the
transformation and prove its correctness. We also briefly report on
preliminary experiments with our prototype implementation. Full proof
details are available as supplemental materials with this submission,
and we plan to submit our implementation and experimental data to the
artifact evaluation committee.

>>>>

Previous algorithms for data-flow analysis are unable to avoid propagating
data-flow facts along infeasible paths that arise in the presence of
correlated polymorphic method calls. 
% 
We present an approach for transforming an IFDS problem into an IDE problem
in which path feasibility is encoded into functions associated
with edges in an exploded control-flow supergraph. The solution to this
IDE problem can be mapped back to the solution space of the original IFDS
problem, and is more precise for some client programs because data flow along
infeasible paths is prevented. We present a formalization of the
transformation, prove its correctness, and briefly report on
preliminary experiments with our prototype implementation. Full proof
details are available in the Appendix,
and we plan to submit our implementation and experimental data to the
artifact evaluation committee. 
%  
As future work, it is possible to adapt our approach to work on IDE
problems. We would convert an initial IDE problem into a more complex IDE problem, 
such that the solution of the latter generates a more precise
solution to former, by preventing data flow along infeasible paths.
